---
title: "Page Visits Funnel"
output: html_notebook
---
Cool T-Shirts Inc. has asked you to analyze data on visits to their website. 
Your job is to build a funnel, which is a description of how many people 
continue to the next step of a multi-step process.

In this case, our funnel is going to describe the following process:

1. A user visits CoolTShirts.com
2. A user adds a t-shirt to their cart
3. A user clicks “checkout”
4. A user actually purchases a t-shirt

```{r message = FALSE, error=TRUE}
# load packages
library(readr)
library(dplyr)
```

```{r message = FALSE, error=TRUE}
# load data
visits <- read_csv("visits.csv")
cart <- read_csv("cart.csv")
checkout <- read_csv("checkout.csv")
purchase <- read_csv("purchase.csv")
```

```{r error=TRUE}
# inspect data frames
head(visits)
head(cart)
head(checkout)
head(purchase)
```

```{r error=TRUE}
# define visits_cart here:



```

```{r error=TRUE}
# define total_visits here:


```

```{r error=TRUE}
# define visit_no_cart here:




```

```{r error=TRUE}
# calculate visit_no_cart_percent here:


```

```{r error=TRUE}
# define cart_checkout here:



```

```{r error=TRUE}
# define total_carts here:


```

```{r error=TRUE}
# define cart_no_checkout here:




```

```{r error=TRUE}
# calculate cart_no_checkout_percent here:


```

```{r error=TRUE}
# define all_data here:





```

```{r error=TRUE}
# define total_checkout here:


```

```{r error=TRUE}
# define checkout_no_purchase here:




```

```{r error=TRUE}
# calculate checkout_no_purchase_percent here:


```

```{r error=TRUE}
# update all_data with time_to_purchase column here:


```

```{r error=TRUE}
# inspect the updated all_data data frame here:

```

```{r error=TRUE}
# define time_to_purchase here:



```