---
title: "A/B Testing for ShoeFly.com"
output: html_notebook
---

Our favorite online shoe store, ShoeFly.com is performing an A/B Test. They have two different versions of an ad, which they have placed in emails, as well as in banner ads on Facebook, Twitter, and Google. They want to know how the two ads are performing on each of the different platforms on each day of the week. Help them analyze the data using aggregate measures.

```{r message = FALSE, error=TRUE}
# load packages
library(readr)
library(dplyr)
```

```{r message = FALSE, error=TRUE}
# load ad clicks data
ad_clicks <- read_csv("ad_clicks.csv")
```

```{r error=TRUE}
# inspect ad_clicks here:
head(ad_clicks)
```

```{r error=TRUE}
# define views_by_utm here:
views_by_utm <- ad_clicks %>%
  group_by(utm_source) %>%
  summarize(count = n()) %>%
  arrange(desc(count))

views_by_utm
```

```{r error=TRUE}
# define clicks_by_utm here:
clicks_by_utm <- ad_clicks %>%
  group_by(utm_source, ad_clicked) %>%
  summarize(count = n())

clicks_by_utm
```

```{r error=TRUE}
# define percentage_by_utm here:
percentage_by_utm <- clicks_by_utm %>% 
  group_by(utm_source) %>%
  mutate(percentage = count/sum(count)) %>%
  filter(ad_clicked == TRUE) %>%
  arrange(desc(percentage))


percentage_by_utm
```

```{r error=TRUE}
# define experiment_split here:
experiment_split <- ad_clicks %>%
  group_by(experimental_group) %>%
  summarize(count = n())

experiment_split
```

```{r error=TRUE}
# define clicks_by_experiment here:
clicks_by_experiment <- ad_clicks %>%
  group_by(ad_clicked, experimental_group) %>%
  summarize(count = n()) %>%
  filter(ad_clicked == TRUE)

clicks_by_experiment
```

```{r error=TRUE}
# define a_clicks here:
a_clicks <- ad_clicks %>%
  select(-user_id) %>%
  filter(experimental_group == 'A')

head(a_clicks)

# define b_clicks here:
b_clicks <- ad_clicks %>%
  select(-user_id) %>%
  filter(experimental_group == 'B')

head(b_clicks)


```

```{r error=TRUE}
# define a_clicks_by_day here:
a_clicks_by_day <- a_clicks %>%
  group_by(day, ad_clicked) %>%
  summarize(count = n())
head(a_clicks_by_day)


# define b_clicks_by_day here:
b_clicks_by_day <- b_clicks %>%
  group_by(day, ad_clicked) %>%
  summarize(count = n())

head(b_clicks_by_day)


```

```{r error=TRUE}
# define a_percentage_by_day here:

a_percentage_by_day <- a_clicks_by_day %>%
  group_by(day) %>%
  mutate(percentage = count/sum(count)) %>%
  filter(ad_clicked == TRUE) #%>%
  #arrange(desc(percentage))


# define b_percentage_by_day here:
b_percentage_by_day <- b_clicks_by_day %>%
  group_by(day) %>%
  mutate(percentage = count/sum(count)) %>%
  filter(ad_clicked == TRUE)# %>%
  #arrange(desc(percentage))

a_percentage_by_day
b_percentage_by_day


```

We can see that ad A outperformed ad B on every day of the week except Tuesday and Sunday. It seems like as A is the better choice for ShoeFly.com!